|

### 2022-12-13 r-report/Paper.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results='hide', message=FALSE, warning=FALSE)
knitr::opts_chunk$set(fig.height = 4, fig.width = 6)
options(knitr.kable.NA = '',knitr.table.format = "latex")
knitr::read_chunk('r-report/Paper.R')
library(kableExtra)
```

```{r init}
```

@@

```{r init}
```
```{r,fig.cap="Per Capita Emissions, by Sector, 1970-2019, China vs. Countries classified by Income Levels"}
YEAR_L = 1970
YEAR_U = 2019
GAS = "GHG"
COUNTRY = "China"

source("r-analysis/data_sector_incomelevel.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_facet_incomelevels_sectors_emissions.R", local = TRUE, print.eval = TRUE)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results='hide', message=FALSE, warning=FALSE)
knitr::opts_chunk$set(fig.height = 4, fig.width = 6)
options(knitr.kable.NA = '',knitr.table.format = "latex")
#knitr::read_chunk('r-report/Paper.R')
library(kableExtra)
```

```{r setup-ex}
source('r-imports/init.R')
source('r-analysis/meta.R')
theme_ghg = function(){
  theme_minimal() %+replace%
     theme(
       plot.title =element_blank(),
       plot.subtitle = element_blank()
    )
}
DIRECT_PLOTTING = F
```

@@

```{r init}
```
```{r,fig.cap="Per Capita Emissions, by Sector, 1970-2019, China vs. Countries classified by Income Levels"}
YEAR_L = 1970
YEAR_U = 2019
GAS = "GHG"

source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
